---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

body {
  font-family: Times;
  color: #333;
}
h2 {
  color: #2c3e50;
  padding-bottom: 5px;
}

```


## Data 

The data was gathered from music listening sessions taken over a week. This captured important details such as intial energy and final energy (ranked 0 to 6), and session duration in minutes.

The following bar chart shows the initial energy of the music listening sessions, and as a response variable its grouped by  the mean duration of the music listening sessions.


```{r}
library(tidyverse)
# Load data
logged_data <- read.csv('https://docs.google.com/spreadsheets/d/e/2PACX-1vRtn8ewxlbvlcvY-O4AXnk8f4c_0nmjhQxei9uqpwI83h2H6yI89d4ROVpfmEUrgQXyuugoGz3At83d/pub?output=csv')

# Rename columns for clarity
latest_data <- logged_data %>% 
  rename(music_software = 1,
         session_start = 2,
         initial_energy = 3,
         duration_minutes = 4,
         genres = 5,
         listening_mood = 6,
         tempo_bpm = 7,
         final_energy = 8,
         location = 9)

mean_duration <- mean(latest_data$duration_minutes)

# Calculate mean duration by initial energy
i_energy_duration <- latest_data %>%
  group_by(initial_energy) %>%
  summarise(mean_duration = mean(duration_minutes))

# Bar chart
ggplot(i_energy_duration, aes(x = as.factor(initial_energy), y = mean_duration, fill = as.factor(initial_energy))) +
  geom_bar(stat = "identity") +
  labs(title = "Average Listening Duration by Initial Energy",
       x = "Initial Energy (1-5)",
       y = "Mean Duration (Minutes)") +
  theme_minimal() +
  scale_fill_brewer(palette = "Set2") +
  theme(legend.position = "none") +
  theme(plot.title = element_text(hjust = 0.5))

```

And the following bar chart shows the same but for final energy.

```{r}

# Calculate mean duration by final energy
f_energy_duration <- latest_data %>%
  group_by(final_energy) %>%
  summarise(mean_duration = mean(duration_minutes))

# Bar chart
ggplot(f_energy_duration, aes(x = as.factor(final_energy), y = mean_duration, fill = as.factor(final_energy))) +
  geom_bar(stat = "identity") +
  labs(title = "Average Listening Duration by Final Energy",
       x = "Final Energy (1-5)",
       y = "Mean Duration (Minutes)") +
  theme_minimal() +
  scale_fill_brewer(palette = "Set3") +
  theme(legend.position = "none") +
  theme(plot.title = element_text(hjust = 0.5))
```


## Understanding the Data from the Charts

### Intial Energy

* Initial energy varies from 0 to 5 because there wasn't a sample
of 6 points of energy, though it was an option.
* Initial energy of 0 has the highest mean duration = `r round(max(i_energy_duration), 1)`
* Initial energy of 5 has the lowest = `r round(min(i_energy_duration), 1)`



### Final Energy 

* Final energy varies from 2 to 6, probably hinting to a trend 
of higher energy after long listening sessions.
* Final energy of 2 has the lowest mean duration = `r round(min(f_energy_duration), 1)`
* Final energy of 6 has the highest = `r round(max(f_energy_duration), 1)`


